---
title: "Project"
output: pdf_document
date: "2023-04-05"
---

# LOAN RISK PREDICTION MODEL USING DECISION TREE

## DATA LOADING
```{r}
data=read.csv("credit_risk_dataset.csv")
```

```{r}
head(data)
```

## DATA PREPROCESSING
```{r}
#Checking for any missing values in the dataset.
sum(is.na(data))
```
There are missing values in the dataset. We need to remove the missing values from the dataset.

```{r}
#Removing rows with missing values
data=na.omit(data)
sum(is.na(data))
```

All the missing values have been removed from the dataset.

```{r}
#Checking the datatype of each column in R
str(data)
```

All the datatypes are correct, So no need of changing. The data pre processing is done.

## DATA VISUALISATION


### PLOTTING A SCATTERPLOT BETWEEN THE INCOME AND LOAN AMOUNT
```{r}
library(ggplot2)
pt=ggplot(data=data)+geom_point(aes(y = data$person_income, x = data$loan_amnt))+labs(y = "Person Income", x = "Loan Amount", title = "Scatterplot of Person Income vs Loan Amount")
print(pt)
```

```{r}
pt2=ggplot(data=data)+geom_boxplot(aes(x = data$loan_grade, y = data$loan_int_rate))+labs(x = "Loan Grade", y = "Loan Interest Rate", title = "Boxplot of Loan Grade vs Loan Interest Rate")
plot(pt2)
```
We can see that the Interest Rates are considerably increasing with the level of Loan Grades.

## DATA SPLITTING

We have a large dataset of nearly 30,000 observations. So we can use more data to train. The preferable ratio will be 90% to training data and 10% to testing data.

```{r}
library(caret)
train_index <- createDataPartition(data$loan_status, p = 0.9, list = FALSE)
train_data <- data[train_index, ] 
test_data <- data[-train_index, ]
```

